Supplementary Materials

### 2023-07-03 manuscript/supplementary.tex
minor ms changes
minor ms changesul

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{figures/supplementary/pred_plot_chr2.pdf}
  \label{suppfig:fit-chr1}
\end{figure}

>>>>

\subsection{Additional Residual Diagnostics}

\begin{figure}[htbp]
  \label{suppfig:resid-b}
  \centering
  \includegraphics[width=0.6\textwidth]{figures/supplementary/b_resid.pdf}
  \caption{Residuals from the CADD 6\% model plotted against the predicted $B(x)$
           value.}
\end{figure}

\begin{figure}[htbp]
  \label{suppfig:resid-pc-fit}
  \centering
  \includegraphics[width=0.6\textwidth]{figures/supplementary/phastcons_resid_lof.pdf}
  \caption{Residuals from the PhastCons Priority model plotted against the
  average LoF selection coefficient across genes in a megabase window
(estimated from \cite{Agarwal2023-un}). These results show that the remaining likely 
selection signal is not dependent on the model used (PhastCons Priority versus CADD 6\%).}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{figures/supplementary/pred_plot_chr1.pdf}
  \label{suppfig:fit-chr1}
\end{figure}

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{figures/supplementary/pred_plot_chr2.pdf}
  \label{suppfig:fit-chr2}
\end{figure}
